The first stable release of BWS still has some not yet resolved problems resulting mostly from shortcomings of integrated technologies as well as the ignoration of standards of web browsers in some situations. One of these problems is the direct embedding of scripts in BWS/HTML documents. While the reading of this embedded script code is possible with Mozilla-based browsers using standard DOM methods and the Internet Explorer after all supports this using the (non-standardized) \texttt{innerHTML} property of \texttt{script} nodes, Opera (and Konqueror?) support neither of these methods. A consequence of this is that applications that are required to run on all of these browsers must not use embedded scripts but only external, referenced ones; as retrievel of these scripts is done browser independent using Java methods, referencing scripts works on all browsers.

\textbf{Another browser-misbehaviour concerns event-handling, which i have leider not evaluated in detail yet.}

A proplem not related to browsers but to the BSF engine implementations is the insufficient support of the \texttt{BSFEngine}'s \texttt{apply()} method that is used to pass scripts to their engines. Some standard \texttt{BSFEngine}s, for example Rhino, do not support the method to its full extent but only evaluate the script passed to them using the \texttt{BSFEngine}'s \texttt{eval()} method that does not support passing parameters to scripts. As a consequence to this, passing parameters to scripts is only available for scripting languages that support the \texttt{apply()} method, for example the BSF4Rexx engines.

%As a consequence to all these problems, BWS is not as browser and scripting language neutral as would be desirable, %however if the problems are bypassed while the application is created, many

