LiveConnect is a technology that interaction between Java, JavaScript and browser plug-ins. It enables calls of Java methods from JavaScript as well as access from Java to the functionality of JavaScript.

The development for Java/JavaScript interaction was started by Netscape Inc. in 1996; it was first availablel with the release of the Netscape Navigator 3.0. Nowadays \footnote{February 2004.} this functionality is provided by the Sun Java Plugin.

For this Java/JavaScript interaction, Netscape provides the \texttt{netscape.javascript.JSObject} Java class that capsules all non-primitive data types passed between JavaScript and Java. This class also provides the only way for Java to access the current documents DOM\footnote{From Java 1.5 on, Sun \emph{will provide} another, better adjusted possibility for accessing the DOM called the \emph{Common DOM API}}. Due to this very generic DOM interface, modifiying the DOM from Java is comparativly elaborate. See figure \ref{fig:JavaJSDomAccess} for a comparison of modifiying a DOM element from Java compared to modifying it from JavaScript.

\begin{figure}[htbp]
Setting the background color of the first heading to red in JavaScript and Java.	
\begin{verbatim}
firstHeading=window.getElementsByTagName("h1")[0];
firstHeading.style.backgroundColor="red;"
\end{verbatim}
JavaScript

\begin{verbatim}
Object[] objectArray=new Object[1];
JSObject appletWindow=this.getWindow();
objectArray[0]="h1";
JSObject headingArray=
  (JSObject)appletWindow.call(getElementsByTagName,objectArray);
JSObject firstHeading=(JSObject)headingArray.getSlot(0);
JSObject styleAttribute=(JSObject)firstHeading.getAttribute("style");
objectArray[0]="red";
styleAttribute.setMember("backgroundColor",objectArray)
\end{verbatim}
Java

	\caption{Comparision of DOM access in Java and JavaScript}
	\label{fig:ComparisionOfDOMAccessInJavaAndJavaScript}
\end{figure}